---
layout: post
title: "Blog with Knitr and Jekyll"
description: ""
category: lessons
tags: [knitr, jekyll, tutorial]
---
{% include JB/setup %}

Notes on creating a [Jekyll-Bootstrap](http://jekyllbootstrap.com/) blog post 
with [knitr](http://yihui.name/knitr/). Knitr is a general-purpose package for 
dynamic report generation in [R](http://www.r-project.org/).
The only required input is an **R Markdown** file. Markdown is a simple 
formatting syntax for authoring web pages. The source file used for this
post is named `2012-07-02-knitr-jekyll.Rmd` 
([source](https://github.com/jfisher-usgs/jfisher-usgs.github.com/blob/master/Rmd/2012-07-02-knitr-jekyll.Rmd)).

From the R Console:
```{r eval=FALSE}
KnitPost <- function(input, base.url = "/") {
  require(knitr)
  opts_knit$set(base.url = base.url)
  fig.path <- paste0("figs/", sub(".Rmd$", "", basename(input)), "/")
  opts_chunk$set(fig.path = fig.path)
  opts_chunk$set(fig.cap = "center")
  render_jekyll()
  knit(input, envir = parent.frame())
}
KnitPost("2012-07-02-knitr-jekyll.Rmd")
```

Move the resulting folder containing figures and the Markdown file (`*.md`) 
into the local Git repository. That's it.
 
Examples of embedding R code:
```{r}
summary(cars)
```

```{r fig1, fig.width=6, fig.height=4, echo=TRUE}
plot(cars)
```
##### Figure 1: Caption.

```{r fig2, fig.width=6, fig.height=5, echo=TRUE}
filled.contour(volcano)
```
##### Figure 2: Caption.
